My title

### 2024-02-08 paper/paper.qmd
pdfs
adding tex

```{r}
#| label: fig-penguins

ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species, shape = sex),
             size = 10,
             alpha = 1) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.9),
    plot.title.position = "plot",
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )

>>>>

```{r}
#| label: fig-penguins
#| fig-cap: Ugly graph

ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species, shape = sex),
             size = 20,
             alpha = .7) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.9),
    plot.title.position = "plot",
    title = element_text(size=24, face='bold'),
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )
